---
title       : Developing Data Products Project Assignment
subtitle    : Reproducible Pitch Presentation
author      : Rawender Guron
job         : Data Science Learner
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, bootstrap, interactive]
mode        : selfcontained # {standalone, selfcontained, draft}
url:
  lib: ./libraries
  assets: ./assets
knit        : slidify::knit2slides
ext_widgets : {rCharts: [libraries/nvd3]}
github:
  user: rawgit
  repo: Developing_Data_Products_Project_Assignment
---
## Introduction

This presentation is part of the project assignment for Coursera Developing Data Products class. This is the second, 'Reproducible Pitch Pressentation', part of the assignment. 

The first part, shiny application, can be viewed on https://rawgit.shinyapps.io/CO2_Emissions, and the code is deposited in https://github.com/rawgit/DDP_PA_1. 

This part's code is deposited in https://github.com/rawgit/DDP_PA_2, and the presentation is hosted on https://rawgit.github.io/DDP_PA_2.

The data used in this presentation has been obtained from [The World Bank](http://data.worldbank.org/indicator/EN.ATM.CO2E.PC).

--- 
## World Per Capita CO2 Emissions (MT)

```{r echo=F, results='asis', message = F}
require(googleVis)
gchart = gvisGeoChart(data = CO2_PC[CO2_PC$Year == 2011,],
                      locationvar = "Country",
                      colorvar = "CO2_MT",
                      options = list(projection="kavrayskiy-vii",
                      width=600, height=400))
print(gchart, tag = 'chart')
```


---

## Major Industrialized Economies Per Capita CO2 Emissions (MT)

```{r echo = F, results = 'asis', message = F}
require(rCharts)
n1 <- nPlot(CO2_MT ~ Year, group = 'Country', type = 'lineChart', 
            data = CO2_PC[CO2_PC$Country %in% c("Australia","Canada","China","European Union","Japan","Russian Federation","United Kingdom","United States")
                          & CO2_PC$Year >= 1990,]
)
n1$print('chart1')
```

--- &radio
## Question

Which 3 major economies respectively are the top 3 per capita CO2 emitters?

1. United States, Australia, and European Union
2. Australia, United States, and China
3. _United States, Australia, and Canada_
4. European Union, United States, and Japan
5. China, United States, and European Union

*** .hint

They are all English speaking countries

*** .explanation

United States, Australia, and Canada


